Causal graph analysis of COVID-19 observational data in German districts reveals effects of determining factors on reported case numbers

### 2021-04-29 manuscript/v6_medrxiv_revision_2/manuscript.Rmd
fix references and update diff tex/diff pdf

```{r rundifflatex, message=FALSE, warning=FALSE, include=FALSE}
# careful, it's always one version behind
# library(latexdiffr)
# latexdiff("../v2_medrxiv/manuscript.tex", "manuscript.tex", "latexdiffrRmd")
# system("latexdiff ../v2_medrxiv/manuscript.tex manuscript.tex > diffRmd.tex")
# tinytex::pdflatex("diffRmd.tex")
```

>>>>

```{r rundifflatex, message=FALSE, warning=FALSE, include=FALSE}
# careful, it's always one version behind
# library(latexdiffr)
# latexdiff("../v2_medrxiv/manuscript.tex", "manuscript.tex", "latexdiffrRmd")
# system("latexdiff ../v5_submission_revision/manuscript_tex4submission.bbl manuscript_tex4submission.bbl > diff.bbl")
# system("latexdiff ../v5_submission_revision/manuscript_tex4submission.tex manuscript_tex4submission.tex > diff.tex")
# tinytex::pdflatex("diffRmd.tex")
```
